### 2013-05-08 menger.tex
starting sorgenfrey side project

  \begin{proposition}
    $X$ is compact if and only if $F \tactwin \mengame{X}$
  \end{proposition}

  \begin{proof}
    Assume $X$ is compact. For each open cover played by $C$, pick the finite subcover.

    Assume $F$ has a winning tactical strategy. For any open cover, have $C$ play only it during the entire game. $F$'s only choice must be a finite subcover.
  \end{proof}

@@

@@

  We require a lemma.

  \begin{lemma}
    There exist injective functions $f_\alpha:\alpha\to\omega$ such that if $\alpha<\beta$, then \[f_\beta\rest\alpha =^* f_\alpha\] that is, $f_\beta\rest\alpha$ and $f_\alpha$ agree on all but finitely many ordinals.
  \end{lemma}

@@

@@

  The question remains:

  \begin{question}
    In general, does $F \markwin \mengame{X}$ imply $X$ is $\sigma$-compact?
  \end{question}

  % Let $\sigma(\mathcal{U},n)$ be $F$'s winning Markov strategy.

>>>>

  \begin{proposition}
    $X$ is compact if and only if $F \tactwin \mengame{X}$ if and only if $F \ktactwin{k} \mengame{X}$
  \end{proposition}

  \begin{proof}
    Assume $X$ is compact. For each open cover played by $C$, pick a finite subcover, and this yields a winning tactical strategy.

    Assume $F$ has a winning $k$-tactical strategy. For any open cover, have $C$ play only it during the entire game. $F$'s only choice must be a finite subcover.
  \end{proof}

@@

  For Menger's game, there is no useful distinction between a $k$-Markov strategy for $F$, and a $2$-Markov strategy.

  But there are spaces for which there is no Markov strategy, but there is a $2$-Markov strategy.

@@

  \begin{lemma}
    There exist injective functions $f_\alpha:\alpha\to\omega$ such that if $\alpha<\beta$, then \[f_\beta\rest\alpha =^* f_\alpha\] that is, $f_\beta\rest\alpha$ and $f_\alpha$ agree on all but finitely many ordinals. (In addition, the range of each $f_\alpha$ is co-infinite.)
  \end{lemma}

  \begin{proof}
    Taken from Kunen (used for the construction of an $\omega_1$-Aronszajn tree).

    We begin with the empty function $f_0:0\to\omega_1$ which satisfies the hypothesis, and assume $f_\alpha$ is defined by induction. Let $f_{\alpha+1} = f_\alpha \cup \{\<\alpha,n\>\}$ where $n$ is not defined for $f_\alpha$, and this satisfies the hypothesis.

    Finally, suppose $\gamma$ is the limit of $\alpha_0,\alpha_1,\dots$, and $f_\alpha$ is defined for $\alpha<\gamma$. Let $g_0=f_{\alpha_0}$, and define $g_n : \alpha_n \to \omega$ to be injective, $g_n=^* f_{\alpha_n}$, and $g_{n+1} \rest \alpha_n = g_n$. $g = \bigcup_{n<\omega} g_n$ is an injective function from $\gamma \to \omega$ and $g =^* f_\alpha$ for $\alpha <\gamma$, but the range need not be coinfinte. So let
    \[
      f_\gamma(\beta) = \left\{
      \begin{array}{ll}
        g(\alpha_{2n}) & \beta = \alpha_n \\
        g(\beta) & \text{otherwise}
      \end{array}
      \right.
    \]
    which frees up $\{g(\alpha_{2n+1}):n<\omega\}$ from the range of $f_\gamma$, but still agrees with all but finitely many points compared to previous $f$'s.
  \end{proof}

@@

  We adapt this result for regular spaces.

@@

  \begin{example}
  Let $R$ be given the topology from example 67 from Counterexamples in Topology, the topology generated by open intervals with or without the rationals removed. This space is non-regular, non-$\sigma$-compact, and Lindel\"of.
  \end{example}

  \begin{proof}
  From Counterexamples: The rationals are closed, but the closure of any open neighborhood is the whole real line, so they cannot be separated from any irrational point. Compact sets in this topology are nowhere dense in the Euclidean topology, so there cannot be countably many which union to the whole space. $\{(a,b)\setminus D : a,b\in\mathbb{Q},D\in\{\emptyset,\mathbb{Q}\}\}$ is a countable base for the space, and second-countability implies Lindel\"of.
  \end{proof}
